\cvsection{Work Experience}
\begin{cventries}

  \cventry
    {FullStack Engineer}
    {Boloo B.V}
    {Eindhoven, Netherlands}
    {Aug. 2020 - Present}
    {
      \begin{cvitems}
        \item {Implemented Complete redesign of User facing dashboard using customised Ant design system.}
        \item {Worked with multiple Design systems such as Ant Design, Material Design and custom design using SASS.}
        \item {Collaborated with the QA team to test and optimise features developed, as well as adding E2E Cypress to our automated testing suites.}
        \item {Improved accessibility by implementing Theming(Dark mode), Internalization, Site wide search(Cmd + K).}
        \item {Integrated Sentry error reporting,ESLint, prettier and Git hooks for maintaining consistent code base.}
        \item {Completely responsible for delivering 3 projects(Internal dashboard, Email campaign, Automated Invoicing).}
        \item {Fully Responsible for building core components, Visualization of Time series data, E2E testing, CI/CD pipelines and frontend deployments.}
      \end{cvitems}
    }

  \cventry
    {FullStack Engineer}
    {Reverence Technologies sp. z o.o}
    {Warsaw, Masovian District, Poland}
    {Nov. 2019 - May. 2020}
    {
      \begin{cvitems}
        \item { Developed frontend features using React, Redux, SSR.}
        \item { Developed minor backend features using Python, Django, DRF.}
        \item { Wrote Cypress E2E tests which covers complete functionalities.}
        \item { Built Order Book visualization , Time series graph using chart.js.}
        \item { Overlooked infrastructure,developed and administered Linux deployment and
        operations solutions using Gitlab CI/CD ,Docker, Nginx.}
        \end{cvitems}
    }

  \cventry
    {Frontend Developer}
    {}
    {}
    {Aug. 2018 - Nov. 2019}
    {
      \begin{cvitems}
        \item { Managed Front-end using React,Redux,styled-components.}
        \item { Implemented a client-side localization system for the entire app.}
        \item { Did Performance optimization and was fully responsible for shipping code to production.}
        \item { Migrated from client side to server side rendering (SSR) which improved SEO score
        significantly.}
        \item { Eliminated Bootstrap and other CSS libraries completely from the application,
        and replaced them with custom styled-components.}
        \end{cvitems}
    }

  \cventry
    {Frontend Developer}
    {}
    {}
    {Nov. 2017 - Aug. 2018}
    {
      \begin{cvitems}
        \item {Did a major re-engineering of the development workflow which led to
        increase in development speed.}
        \item {Responsible for making bug-fixes in existing web application.}
        \item {Used Angular,RxJS,Ngx-Bootstrap,HTML 5,CSS 3.}
        \end{cvitems}
    }

    
  \cventry
    {Frontend Developer(CONTRACT)}
    {Anulom Technologies Pvt Ltd}
    {Coimbatore, Tamil Nadu, India}
    {Aug. 2017 - Nov. 2017}
    {
      \begin{cvitems}
        \item { Implemented AWS S3 storage support for the application.}
        \item { Successfully delivered a mobile application in two month time.}    
        \item { Developed an Hybrid Application from scratch using Angular 4,Ionic 3.0.}
        \end{cvitems}
    }

  \cventry
    {Frontend Developer}
    {iamneo (Formerly Examly)}
    {Bengaluru, Karnataka, India}
    {Jun. 2016 - Jul. 2017}
    {
      \begin{cvitems}
        \item {Managed Front-end using Bootstrap, Angular 2,Typescript , HTML5, CSS3.}
        \item {Developed Hybrid mobile application from scratch using Ionic framework.}
        \item {Introduced and enforced a consistent coding style across the application.}
        \item {Crafted a solid design system to enforce consistency across the application.}
      \end{cvitems}
    }


\end{cventries}
